``Interestingness'' in Mathematical Theory Exploration

### 2019-04-29 PhDThesis/bucketing.tex
Include bucketing tex file in thesis

\begin{enumerate}
  \item Define the \emph{signature selection problem} for theory exploration.
  \item Analyse the performance of theory exploration on the TEBenchmark problem
    set.
  \item Analyse the effect of signature selection on the quantity of desirable properties
    attainable by theory exploration on this problem set.
  \item Demonstrate how the signature selection problem is distinct from the well-know
    \emph{clustering problem} in machine learning, and how clustering algorithms
    cannot be directly applied to signature selection.
\end{enumerate}

@@

As an example, giving the definitions from Figure~\ref{fig:haskellexample} to
\qspec{}, along with suitable comparison functions, random data generators and
variables \hs{n :: Nat} and \hs{b :: Bool}, will give rise to an equivalence
class for each type \hs{Nat}, \hs{Bool}, \hs{Nat -> Nat}, \hs{Nat -> Bool} and
\hs{Bool -> Bool}. Testing will find unequal terms in some of these classes
(such as the \hs{Bool} class containing \hs{True}, \hs{False}, \hs{b},
\hs{not b}, \hs{odd n} and \hs{even n}, which are all mutually unequal), split
them up, and repeat until no more splits are found. Equations are then generated
between elements of non-singleton classes, such as $\{\text{\hs{odd n}},
\text{\hs{not (even n)}}, \text{\hs{not (not (odd n))}}, \ldots\}$, and reduced
to a minimal set (for example, discarding \hs{odd n == not (not (odd n))} as an
instance of the more general \hs{b == not (not b)}). The remaining equations
(including \hs{not (not b) == b} and \hs{not (odd n) == even n}, etc.) are
output, either for the user to peruse or for another system to process, like the
\textsc{HipSpec} automated theorem prover.

@@

We follow the tradition of prior practitioners and use an existing corpus of
theorems as a \emph{ground truth} against which to compare results. To analyse
behaviour on large inputs (i.e. those for which exploration is currently
infeasible), as required to study the effects of signature selection, we have used the
\tebenchmark{} of section~\ref{sec:tebenchmark}, which is based on the Tons of
Inductive Problems (TIP) problem set for theorem provers~\cite{claessen2015tip}.

>>>>

\begin{enumerate}
  \item Define the \emph{signature selection problem} for theory exploration.
  \item Analyse the performance of theory exploration on the Theory Exploration
    Benchmark.
  \item Analyse the effect of signature selection on the quantity of desirable properties
    attainable by theory exploration on this problem set.
  \item Demonstrate how the signature selection problem is distinct from the well-know
    \emph{clustering problem} in machine learning, and how clustering algorithms
    cannot be directly applied to signature selection.
\end{enumerate}

@@

As an example, giving the definitions from Figure~\ref{fig:haskellteexample} to
\qspec{}, along with suitable comparison functions, random data generators and
variables \hs{n :: Nat} and \hs{b :: Bool}, will give rise to an equivalence
class for each type \hs{Nat}, \hs{Bool}, \hs{Nat -> Nat}, \hs{Nat -> Bool} and
\hs{Bool -> Bool}. Testing will find unequal terms in some of these classes
(such as the \hs{Bool} class containing \hs{True}, \hs{False}, \hs{b},
\hs{not b}, \hs{odd n} and \hs{even n}, which are all mutually unequal), split
them up, and repeat until no more splits are found. Equations are then generated
between elements of non-singleton classes, such as $\{\text{\hs{odd n}},
\text{\hs{not (even n)}}, \text{\hs{not (not (odd n))}}, \ldots\}$, and reduced
to a minimal set (for example, discarding \hs{odd n == not (not (odd n))} as an
instance of the more general \hs{b == not (not b)}). The remaining equations
(including \hs{not (not b) == b} and \hs{not (odd n) == even n}, etc.) are
output, either for the user to peruse or for another system to process, like the
\textsc{HipSpec} automated theorem prover.

@@

We follow the tradition of prior practitioners and use an existing corpus of
theorems as a \emph{ground truth} against which to compare results. To analyse
behaviour on large inputs (i.e. those for which exploration is currently
infeasible), as required to study the effects of signature selection, we have
used the Theory Exploration Benchmark of section~\ref{sec:tebenchmark}, which is
based on the Tons of Inductive Problems (TIP) problem set for theorem
provers~\cite{claessen2015tip}.
